---
title: Part 1 <!-- Give an appropriate title -->
author: Song Kim
---

<!-- Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials. You should

    Show the sample mean and compare it to the theoretical mean of the distribution.
    Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
    Show that the distribution is approximately normal. 
In point 3, focus on the difference between the distribution of a large collection of random exponentials and 
    the distribution of a large collection of averages of 40 exponentials.
    
    Did you show where the distribution is centered at and compare it to the theoretical center of the distribution?
    Did you show how variable it is and compare it to the theoretical variance of the distribution?
    Did you perform an exploratory data analysis of at least a single plot or table highlighting basic features of the data?
    Did the student perform some relevant confidence intervals and/or tests?
    Were the results of the tests and/or intervals interpreted in the context of the problem correctly?
    Did the student describe the assumptions needed for their conclusions? -->

## Overview
<!-- Overview: In a few (2-3) sentences explain what is going to be reported on. -->

## Simulations
<!-- Simulations: Include English explanations of the simulations you ran, with the accompanying R code. 
    Your explanations should make clear what the R code accomplishes. -->

```{r sims}
set.seed(94692)
sim <- rep(NA, 1000)
for (i in c(1:1000)) {
    sim[i] = mean(rexp(40, 0.2))
}
```
After setting a seed for the random number generator, 1000 samples of 40 numbers were drawn from an exponential distribution with lambda=0.2. The average was taken for each of the samples.

## Sample Mean vs. Theoretical Mean
<!-- Sample Mean versus Theoretical Mean: Include figures with titles. In the figures, highlight the means you are comparing. 
    Include text that explains the figures and what is shown on them, and provides appropriate numbers. -->

```{r mean}
mean(sim)
```
The sample mean of these 1000 means is 5.040, while the expected mean of this distribution is $$\frac{1}{0.2} = 5.$$

## Sample Variance vs. Theoretical Variance
<!-- Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. 
    Include text that explains your understanding of the differences of the variances. -->

```{r var}
var(sim)
```
The variance of this distribution is 0.6498, while the expected variance is $$\frac{(1/0.2)^2}{40}=0.625.$$

## Distribution
<!-- Distribution: Via figures and text, explain how one can tell the distribution is approximately normal. -->

```{r norm}
# histogram
h <- hist(sim, xlab="Mean of sample from exponential distribution, n=40", ylim=c(0,260), main="Means of 40 samples")
# create theoretical sampling distribution
xfit <- seq(0, 8, length = 50) 
yfit <- dnorm(xfit, mean = 5, sd = 5/sqrt(40)) 
yfit <- yfit * diff(h$mids[1:2]) * length(sim) 
lines(xfit, yfit, col = "red", lwd = 2)
# legend
legend("topright", legend=c("Theoretical\ndistribution\n"), col="red", lwd=2)
# mean markers
abline(v = mean(sim), lwd=2)
abline(v = 5, col="red", lwd=2)
```
The above histogram shows the distribution of the means of the 40 samples collected. By the Central Limit Theorem, this sampling distribution should be approximately normal. This is, at least visually, confirmed when comparing the histogram to the theoretical Normal distribution of the means (shown in red).